\bf On semidefinite-representable sets over valuation fields

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

\begin{algorithm}
    \caption{\textbf{SOLVELP}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
      \STATE find $x_0$ such that $Dx_0=e$
      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
      \ENDIF
      \IF{$A$ not in Smith Normal Form}
      \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
      \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}}
      \ELSE
      \STATE
      \STATE
      \RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
      \ENDIF
    \end{algorithmic}
\end{algorithm}

@@

  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$,
  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
  In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$. Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}. 
\end{proof}

>>>>

\begin{algorithm}
    \caption{\textbf{SOLVELP}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
      \STATE find $x_0$ such that $Dx_0=e$
      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
      \ENDIF
      \IF{$A$ not in Smith Normal Form}
      \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
      \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}}
      \ELSE
      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$}
      \STATE STATUS $\leftarrow$ FEAS
      \STATE give solution in this case
      \ENDIF
      \STATE
      \STATE
      \RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
      \ENDIF
    \end{algorithmic}
\end{algorithm}

@@

  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$,
  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
  In particular, for all $n \in \mathbb{N}$ if we set $\alpha_n = -({\langle c', y^* \rangle + \pi^{-n}})/{c'_i}$,
  we have $\val \left(\langle c', y^* + \alpha_n e ^i \rangle\right) = \val \pi^{-n} = -n$.
  Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}.
\end{proof}
